---
title: "Stats Activity Intro EDS"
output: html_document
date: "2022-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the tidyverse package using the library() function.

```{r}

```

Use read_csv() to load the NYC_airquality.csv file. Call it airqual.

These data are a slightly edited version of the dataset linked below. You can read about the data there. 
https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/airquality.html

```{r}

```

Use summarize() to show the mean and standard deviation of Ozone and Solar.R (careful with NAs)

```{r}

```

Use group_by() and summarize() to output the mean Ozone, Solar.R, and Wind PER MONTH. Careful with NAs. None of the results should be an NA.

```{r}

```

Use ggplot to make a histogram of Ozone concentrations.

Describe the ozone distribution. Do you think it is normal? Is it skewed?
Replace this text with your answer.

```{r}

```

Show a histogram of wind. Describe the distribution. Is it normal? Is it skewed?
Replace this text with your answer.

```{r}

```

Make a good plot of Ozone through time. Ozone is measured in ppb.

When was the worst air quality in NYC in 1973? 
Replace this text with your answer.

Use the internet to look up the meaning of these Ozone levels, are they bad? 
Replace this text with your answer.

```{r}

```

Use ggplot to explore the relationships between Ozone and Solar Radiation, Wind, Temp, Month, and Day.

Which of these has the best relationship with Ozone? Show your plot. 

Search the internet for an answer: Why is Ozone related to the parameter you chose?
Replace this text with your answer

```{r}

```

